---
title: "Data Collection-Week 7-misinformation"
author: "Ruiping Ma"
date: "2024-03-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

misinfo_d <- read.csv('../data/life-under-lockdown-wave2-extract.csv')
```

# Association of number of misinformation beliefs with gender
## Hypothesis
It was hypothesised that number og misinformation beliefs would be associated with gender.

## Methodology
Welth's t-text was used to compare mean numbers of misinformation beliefs for participants.


```{r}
misinfo_d %>%
  ggplot(aes(x = beliefs))+
  geom_histogram(bins=6)
```


```{r}
misinfo_d %>%
  ggplot(aes(x = gender))+
  geom_bar()
```

```{r}
mean(misinfo_d$beliefs)
```
```{r}
misinfo_d %>%
  filter(gender %in% c('Female','male')) %>%
  t.test(formula = beliefs ~ gender, data = . )
```


In the sample, males had more misinformation beliefs(M=0.73) than females (M=0.61), but this was not statistically significant, t(491.31) = -1.201, p=0.230.
问题：关于最后的t-text编写，p-value是什么意思，以及其他数据是什么意思。

# Association of number of misinformation beliefs with age
## Hypothesis
It was hupothesised that number of information beliefs would be positively associated with age.

## Methodology
The product-moment (or Pearson) coffelation between number of misinformation 

## Findings
```{r}
misinfo_d %>%
  cor.test(
    formula = ~beliefs + age,
    data =.,
    method = 'pearson'
  )

```

There was a statistically significant moderate negative correlation between number of misinformation beliefs and age, r(498) = -.24, p < .001.

# Association of number of misinformation beliefs with amount of knowledge gathered from Facebook
## Hypothesis
It was hypothesised that there would be a positive correlation between number of misinformation beliefs and amount of knowledge gathered from Facebook

## Methodology
The rank-moment (or Pearson) coffelation between number of misinformation 

## Findings
```{r}
misinfo_d %>%
  ggplot(aes(x = age, y = beliefs)) +
  geom_jitter()


```